Market Simulator

### 2020-08-13 analysis/05_market_simulator.Rmd
Building out more of the persona reactive element. Need to create the empty dataframe for it with appropriate levels to correspond with the input questions.

# Persona Reactive Element
p <- reactive({
  #Amnesty International
    beta$p1_value <- 0
    beta$p1_value[beta$levels == 'Persona 1'] <- 1
    beta$p1_value[beta$levels %in% input$p1_charity_importance] <- 1
    beta$p1_value[beta$levels %in% input$p1_trust_in_charity] <- 1
    beta$p1_value[beta$levels %in% input$p1_donation_frequency] <- 1
    beta$p1_value[beta$levels %in% input$p1_donation_amount] <- 1
    beta$p1_value[beta$levels %in% input$p1_volunteer_12] <- 1
  #Greenpeace
    beta$p2_value <- 0
    beta$p2_value[beta$levels == 'Persona 2'] <- 1
    beta$p2_value[beta$levels %in% input$gp_issue] <- 1
    beta$p2_value[beta$levels %in% input$gp_fin_trans] <- 1
    beta$p2_value[beta$levels %in% input$gp_account] <- 1
    beta$p2_value[beta$levels %in% input$gp_funding] <- 1
    beta$p2_value[beta$levels %in% input$gp_gov_relat] <- 1
  #Oxfam
    beta$p3_value <- 0
    beta$p3_value[beta$levels == 'Persona 3'] <- 1
    beta$p3_value[beta$levels %in% input$ox_issue] <- 1
    beta$p3_value[beta$levels %in% input$ox_fin_trans] <- 1
    beta$p3_value[beta$levels %in% input$ox_account] <- 1
    beta$p3_value[beta$levels %in% input$ox_funding] <- 1
    beta$p3_value[beta$levels %in% input$ox_gov_relat] <- 1
    beta

@@

```{r sidebar inputs, echo=FALSE}

@@

Organization Breakdown {.tabset .tabset-fade}
--------------------------------------------------
### Org 1

@@

@@

selectInput("international_news",
         label = "Follow international news:",
         choices = c('Multiple times a day',
                     'Every day',
                     "Once a week",
                     "Hardly ever",
                     "Never"))

selectInput("political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("international_news",
         label = "Follow international news:",
         choices = c('Multiple times a day',
                     'Every day',
                     "Once a week",
                     "Hardly ever",
                     "Never"))

@@

selectInput("international_news",
         label = "Follow international news:",
         choices = c('Multiple times a day',
                     'Every day',
                     "Once a week",
                     "Hardly ever",
                     "Never"))

>>>>

####################################################################

beta <- as.data.frame(matrix(rep(0), nrow = 28))

beta$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "filler","filler", "filler", "filler", "filler", "filler","filler", "filler", "filler", "filler", "filler","filler", "filler", "filler", "filler", "filler","filler", "filler", "filler", "filler")

# Persona Reactive Element
p <- reactive({
  #Persona 1
    beta$p1_value <- 0
    beta$p1_value[beta$levels == 'Persona 1'] <- 1
    beta$p1_value[beta$levels %in% input$p1_charity_importance] <- 1
    beta$p1_value[beta$levels %in% input$p1_trust_in_charity] <- 1
    beta$p1_value[beta$levels %in% input$p1_donation_frequency] <- 1
    beta$p1_value[beta$levels %in% input$p1_donation_amount] <- 1
    beta$p1_value[beta$levels %in% input$p1_volunteer_12] <- 1
  #Persona 2
    beta$p2_value <- 0
    beta$p2_value[beta$levels == 'Persona 2'] <- 1
    beta$p2_value[beta$levels %in% input$p2_charity_importance] <- 1
    beta$p2_value[beta$levels %in% input$p2_trust_in_charity] <- 1
    beta$p2_value[beta$levels %in% input$p2_donation_frequency] <- 1
    beta$p2_value[beta$levels %in% input$p2_donation_amount] <- 1
    beta$p2_value[beta$levels %in% input$p2_volunteer_12] <- 1
  #Persona 3
    beta$p3_value <- 0
    beta$p3_value[beta$levels == 'Persona 3'] <- 1
    beta$p3_value[beta$levels %in% input$p3_charity_importance] <- 1
    beta$p3_value[beta$levels %in% input$p3_trust_in_charity] <- 1
    beta$p3_value[beta$levels %in% input$p3_donation_frequency] <- 1
    beta$p3_value[beta$levels %in% input$p3_donation_amount] <- 1
    beta$p3_value[beta$levels %in% input$p3_volunteer_12] <- 1
    beta

@@

```{r sidebar inputs commented}

@@

Organizations and Personas {.tabset .tabset-fade}
--------------------------------------------------
### Org 1

@@

selectInput("p1_charity_importance",
          label = "Charity Importance:",
          choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("p1_trust_in_charity",
            label = "Charity Trust:",
            choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("p1_donation_frequency",
         label = "Donation Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months',
                     'Once every six months',
                     'Once a year',
                     'Once every few years',
                     'Never'))

selectInput("p1_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'))

selectInput("p1_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("Yes", "No"))

selectInput("p1_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months',
                     'Once every six months',
                     'Once a year',
                     'Once every few years',
                     'Never'))

selectInput("p1_personal_activism",
         label = "Personal Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

selectInput("p1_family_activism",
         label = "Family Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

selectInput("p1_religious_member",
         label = "Church Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p1_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p1_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p1_labor_member",
         label = "Labor Union Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p1_political_member",
         label = "Political Party Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p1_environmental_member",
         label = "Enviornmental Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p1_professional_member",
         label = "Professional Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p1_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p1_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p1_other_member",
         label = "Other Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p1_national_news",
         label = "Follow national news:",
         choices = c('Multiple times a day',
                     'Every day',
                     "Once a week",
                     "Hardly ever",
                     "Never"))

selectInput("p1_international_news",
         label = "Follow international news:",
         choices = c('Always',
                     "Sometimes",
                     "Never"))

selectInput("p1_news_medium",
         label = "Medium to follow news:",
         choices = c('TV',
                     'Print',
                     "Online",
                     "Social Media",
                     "Radio",
                     "Email newsletters",
                     "News app"))

selectInput("p1_follow_gov",
         label = "Follow government & public affairs:",
         choices = c('Most of the time',
                     'Some of the time',
                     "Only now and then",
                     "Hardly at all"))

selectInput("p1_travel_developing",
         label = "Travel to developing country:",
         choices = c('Yes', 'No'))

selectInput("p1_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("p1_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("p1_others_charitable",
         label = "People should be more charitable:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("p1_worship_attendance",
         label = "Worship service attendance:",
         choices = c('Multiple times a week',
                     'Once a week',
                     "Once a month",
                     "Once a year",
                     "Never"))

selectInput("p1_religion_importance",
         label = "Importance of religion:",
         choices = c('Extremely important',
                     'Very important',
                     'Moderately important',
                     'Slightly important',
                     'Not at all important'))

selectInput("p1_religion",
         label = "Religion:",
         choices = c('Catholic',
                     'Protestant',
                     'Christian Orthodox',
                     'Jewish',
                     'Muslim',
                     'Sikh',
                     'Hindu',
                     'Buddhist',
                     'Atheist',
                     'Other'))

selectInput("p1_gender",
         label = "Gender:",
         choices = c("Male",
                     "Female",
                     "Transgender",
                     "Prefer not to say",
                     "Other"))

selectInput("p1_marital_status",
         label = "Marital Status:",
         choices = c("Married",
                     "Widowed",
                     "Divorced",
                     "Separated",
                     "Never married"))

selectInput("p1_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate degree",
                     "Doctorate"))

selectInput("p1_income",
         label = "Income:",
         choices = c('Less than $10,000',
                     '$10,000 to $19,999',
                     '$20,000 to $29,999',
                     '$30,000 to $39,999',
                     '$40,000 to $49,999',
                     '$50,000 to $59,999',
                     '$60,000 to $69,999',
                     '$70,000 to $79,999',
                     '$80,000 to $89,999',
                     '$90,000 to $99,999',
                     '$100,000 to $149,999',
                     '$150,000 to $199,999',
                     '$200,000 to $299,999',
                     '$300,000 or more'))

selectInput("p1_race",
         label = "Race(s):",
         choices = c('White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other'),
         multiple = TRUE)

selectInput("p1_age",
         label = "Age:",
         choices = c('Under 18',
                     '18 - 24',
                     '25 - 34',
                     '35 - 44',
                     '45 - 54',
                     '55 - 64',
                     '65 - 74',
                     '75 - 84',
                     '85 or older'))

@@

@@
